# EDA
Firstly, we load the data and convert all character variables to factor variables. 
```{r}
library(caret)
library("ggplot2")                     
library("GGally")
library(corrplot)
heart = read.csv('heart.csv')
heart$Sex=as.factor(heart$Sex)
heart$ChestPainType=as.factor(heart$ChestPainType)
heart$ExerciseAngina=as.factor(heart$ExerciseAngina)
heart$ST_Slope=as.factor(heart$ST_Slope)
heart$RestingECG=as.factor(heart$RestingECG)
str(heart)
head(heart,5)
```

Let examine the data first, Here is te correlogram of all the numeric variables of the data. 
```{r}
factor_cols <- sapply(heart, is.factor)
num_cols <- sapply(heart, is.numeric)
df_factor <- heart[, factor_cols]
df_num <- heart[, num_cols]
corrplot(cor(df_num), title = "Numerical Variables Correlation Plot", mar=c(0,0,1,0))
ggpairs(df_factor, title = "Facotr Variables Correlogram")
```


Based on the result, we can see that there are some correlations between variables. Hence, I decide to include the linear model, logiatic models and the ramdom forest model as candidate models. 


To build and test the models, we split data with 80/20. 

```{r}
set.seed(5293)
train_split <- createDataPartition(heart$HeartDisease, p = 0.80, list = FALSE)
train_data <- heart[train_split,]
test_data <- heart[-train_split,]
```